\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Akash Sarkar} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+91 9932897100 \\ Cooch Behar, West Bengal \\ akashsarkarcob98@gmail.com} 
\address{\href{mailto:akashsarkarcob98@gmail.com}{} \\ \href{https://www.linkedin.com/in/akash-sarkar59}{linkedin.com/in/akash-sarkar59} \\ \href{https://github.com/akashsarkar1998}{github.com/akashsarkar1998} \\ 
\href{https://www.hackerrank.com/profile/Akash_59 }{hackerrank.com/profile/Akash_59 }}  %

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{OBJECTIVE}

{Python Developer skilled in various Python libraries, object-oriented programming, and data modeling and cleaning. Passionate about machine learning, adept at solving complex problems, and dedicated to delivering innovative solutions.}


\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Bachelor of Technology}, Siliguri Institute of Technology  \hfill {2016 - 2020}\\
Electrical Engineering
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming Language & Python, Basic HTML and CSS\\
Fundamentals & OOP, Parallel Programming, Data Structures, Data Modelling and Cleaning \\
Libraries & Various libraries like Pandas, Numpy, requests, re etc.\\
Frameworks & Django, Rest, PyTest, Robot Framework, API \\
Database & MySQL\\
Version Control & Git, GitHub, Git Bash \\
Others & Basic Networking, PLC, SCADA, MMI, Product Development \\
\end{tabular}\\
\end{rSection}
\begin{rSection}{EXPERIENCE}

\textbf{Python Developer} \hfill Feb 2024\\
Shutter Technologies Pvt Ltd \hfill \textit{Kolkata, West Bengal}
\item {Developing a product which could simplify web development for both individual developers and companies. Proficient in Python for product development, with understanding the requirements, giving proper solutions, and implementing efficient algorithms. Delivering high-quality products that consistently meet our objectives with innovation. }
 
\textbf{Python Developer} \hfill Dec 2023 - Jan 2024\\
Codepoetry \hfill \textit{Siliguri, West Bengal}
\item Developed and deployed machine learning models on Raga AI platform, including data preparation csv parsing and schema definition. JSON integrated test case execution, and automated drift detection. Proficient in model development, testing, and monitoring on Raga AI platform.

\textbf{Resident Engineer} \hfill Dec 2020 - Dec 2021\\
Yokogawa India Limited \hfill \textit{Arunachal Pradesh}
\item Managed operations at IOCL Depot as an Automation Engineer, focusing on PLC, SCADA, and field instruments. Implemented preventive maintenance strategies, promptly resolving automation system issues to improve facility efficiency and reliability. Led a large team to maintain and to improve facility.

\textbf{Research Analyst} \hfill Jan 2017 - Jan 2019\\
Globsyn AI workspace \hfill \textit{Kolkata, West Bengal}
\item Worked with diverse teams to gather crucial data for AI projects sing Amazon Mechanical Turk for dataset collection and validation. Maintained strict adherence to ethical standards and industry practices to safeguard data privacy and security.
\end{rSection} 

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\clearpage % New page
\begin{rSection}{PROJECTS}
\vspace{-1.25em}
\item \textbf{Automated API-End Points accessibility checker} {My project can verify the accessibility of APIs or end-points behind the base URL/IP address user provides and watch system meticulously examines each embedded APIs or end points concurrently. Also gives a report to ensuring a smooth digital journey for you and your developer team \href{https://github.com/akashsarkar1998/Automated-API-End-Points-accessibility-checker}{(Github link)}}
\item \textbf{Pandas Data Cleaning Project} {Build a project focusing on filtering, clean and process any file. Goal is efficient data manipulation, achieved through Pandas powerful functionalities.\href{https://github.com/akashsarkar1998/Data_Cleaning_with_Pandas}{(GitHub link)}}
\item \textbf{Encrypting plain text messages} {Build this project, cipher is a method of encrypting alphabetic text by using a simple form of poly alphabetic substitution. \href{https://github.com/akashsarkar1998/Vigenere_Cipher}{(GitHub link)}}
\item \textbf{Car-Counting Prototype} {This project is based on counting car numbers from a live CCTV. Used Open-CV, YOLO Configuration.\href{https://github.com/akashsarkar1998/Counting-car}{(GitHub link)}}
\end{rSection} 

%----------------------------------------------------------------------------------------
\begin{rSection}{TRAINING and CERTIFICATE} 
\begin{itemize}
\item \href{https://drive.google.com/file/d/1S80YoSIyEC577ILkw-U3R8CC6lB_x2s1/view?usp=sharing}{Python Programming Specialization} from University of Michigan, Coursera 
\item \href{https://drive.google.com/file/d/1u-2ycUNbPSwE-oHvkoV9IxXkwhxYAgqt/view?usp=sharing}{Python for Everybody and Data Structure} from University of Michigan, Coursera 
\item\href{https://drive.google.com/file/d/1xRGpsYine5Z89apyTkO5RAcnx0lgeZuL/view?usp=sharing}{Python Certificate by HackerRank} from HackerRank, where I solved various Python problems
\item\href{https://drive.google.com/file/d/1IvGnWsXbfatwdw3qGtuJER2p9oeqYfb1/view?usp=sharing}{Problem Solving Certificate by HackerRank} from HackerRank, where I used Python language to solve various problems
\item\href{https://drive.google.com/file/d/1zim8vkHaI1QXAcOedzDCrten2WmU4wmD/view?usp=drive_link}{Python Programming} from University of Michigan, Coursera 
\item \href{https://drive.google.com/file/d/1bRp-wd0o1pFwUrInKzG33zYrfKQbtzlo/view?usp=sharing}{IBM Data Structure} from Coursera
\end{itemize}
\end{rSection}

%----------------------------------------------------------------------------------------

\begin{rSection}{Extra-Curricular Activities} 
Executive Member, Electrical Engineering Society, Siliguri Institute of Technology
\begin{itemize}
    \item  Collaborated on innovative projects, social work, and cultural programs.
\end{itemize}
Student Representative, National Service Scheme
\begin{itemize}
    \item Organized cloth distribution and blood donation camps in the local community.
\end{itemize}
Achievements:
\begin{itemize}
    \item First position in the photography competition at Siliguri Institute of Technology (2019).
    \item Third position in the Badminton tournament at Siliguri Institute of Technology (2018).
\end{itemize}
\end{rSection}

%----------------------------------------------------------------------------------------

\begin{rSection}{HOBBIES and INTERESTS} 
\begin{itemize}
    \item 	Photography, Mythology and Fictional Books, Art, Badminton, Volleyball.
\end{itemize}
\end{rSection}

\begin{rSection}{LANGUAGES KNOWN} 
\begin{itemize}
    \item English, Hindi, Bengali.
\end{itemize}
\end{rSection}

%----------------------------------------------------------------------------------------
% \begin{rSection}{Leadership} 
% \begin{itemize}
%     \item Admin for the \href{https://discord.com/invite/WWbjEaZ}{FAANGPath Discord community} with over 6000+ job seekers and industry mentors. Actively involved in facilitating online events, career conversations, and more alongside other admins and a team of volunteer moderators! 
% \end{itemize}
% \end{rSection}


\end{document}
